---
title: "Environmental_Project"
author: "Ama Agyemang"
---

A governement agency has provided environmental data from multiple cities to be monitored and analysed.

Loading the data to inspect its structure and explore it

```{r}
#importing package to enable us read the data
library(readr)

#importing package to enable us explore the dataset
library(dplyr)


library(visdat)

library(lubridate)

#import the environmental data set 
envdata <- read_csv("data/Environmental_Data.csv")


str(envdata)
head(envdata)
tail(envdata)

glimpse(envdata)
summary(envdata)

#Viewing 10% of random data within the dataset
sample_frac(envdata, 0.1)

ncol(envdata)
nrow(envdata)
dim(envdata)
names(envdata)

#This is to find out if the dataset has missing values
vis_miss(envdata)




```

Calculating the monthly average temperature for each city

```{r}

  avg_temp_per_city<- envdata %>%
  mutate(YearMonth = floor_date(Date, "month")) %>%
  group_by(City, YearMonth)  %>%
  summarise(Average_temperature = mean(Temperature))

 
  View(avg_temp_per_city)
 
  
```

Viewing the temperature trends across cities using the line plot

```{r}


library(ggplot2)

    avg_temp_per_city %>% 
    ggplot(aes(x=YearMonth, y=Average_temperature, colour=City)) +
    geom_point()+
    geom_line()+
    labs(title="Temperature trends across cities",
         x ="Date (Year-Months)",
         y ="Average Temperature") +
    theme_minimal()
```



Histogram to visualize the distribution of daily rainfall across all cities. Discuss trends & identify extreme values.

```{r}

  envdata %>%
  ggplot(aes(x = Rainfall, fill = City)) +
  geom_histogram(binwidth = 5, alpha = 0.7, position = "identity") +
  labs(title = "Histogram showing Distribution of daily rainfall across all cities",
       x = "Cities", 
       y = "Rainfall") +
  theme_minimal()

```


Scatterplot to analyze the relationship between temperature and humidity. Add a regression
line to interpret the correlation.

```{r}

```












